---
title: "Final Monopoly Report"
output: word_document
date: "2023-05-03"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("C:/Users/Maddie's Laptop/Documents/STAT 345/Projects/STAT345-SP23/Final Project/STAT345---Final/source_monopoly_code.R")
```

## 1. Rules!

-   Before starting the game, it is important to take note of the
    different types of "equipment" in Monopoly. \### Equipment

#### The Board

-   The Board consists of...
    -   40 tiles, each of which have unique actions associated with them
        based on their type.
    -   16 "CHANCE CARDS"
    -   16 "COMMUNITY CHEST CARDS"
    -   2 six-sided dice

#### Types of Tiles

-   "PROPERTY" Tiles

    -   There are 8 different sets of properties
    -   Each set of properties has...
        -   its own color
        -   2 or 3 properties
    -   These tiles can bought
    -   Each of these tiles have a specialized cost/profit associated
        with them
    -   **These tiles can generate a profit**

-   "RAILROAD" Tiles

    -   There are 4 different railroads evenly spaced across the Board
    -   These tiles can be bought
    -   Each of these tiles have a specialized cost/profit associated
        with them
    -   **These tiles can generate a profit**

-   "UTILITY" Tiles

    -   There are two utility tiles
    -   These tiles can be bought
    -   Each of these tiles have a specialized cost/profit associated
        with them
    -   **These tiles can generate a profit**

-   "CHANCE" Tiles

    -   There are 3 chance tiles
    -   If one of these tiles is landed on, a "CHANCE CARD" is drawn
        -   each of these cards has a specialized action associated with
            them

-   "COMMUNITY CHEST" Tiles

    -   There are 3 community chest tiles
    -   If one of these tiles is landed on, a "COMMUNITY CHEST CHEST" is
        drawn
        -   each of these cards has a specialized action associated with
            them

-   "TAX" Tiles

    -   There are 2 tax tiles
    -   Each of these tiles has a cost associated with them

-   "GO"

    -   This is the first tile
    -   Every time this tile is landed on or passed the player collects
        "\$200"

-   "IN JAIL"

-   "GO TO JAIL"

    -   When landed on, the player is moved to "IN JAIL"

-   "FREE PARKING"

#### Moving around the Board and Generating Profits

-   The first step for beginning the game, even before getting to move
    the first game piece, is to determine which player will move first.

    -   To do this, each player will roll both dice and find the sum of
        the rolls. The player with the largest sum will start the game.
        Then the following turn will be the next player.
        -   i.e. if Player 2 starts, Player 3 will go next, then Player
            4, then Player 4, then back to Player 2, and so on...

-   All players will start on the "GO" tile.

-   To determine how many spaces to move, on their turn each player will
    roll both dice and find the sum of the rolls. They will then move
    forward that number of tiles.

    -   In the special case of rolling "doubles" (the roll of each die
        are equal),
        -   the player will find the sum of rolls and move forward this
            number of tiles
        -   then, the player will roll again and repeat the previous
            step.
            -   If the player rolls "doubles" again, repeat the previous
                two steps.
            -   If the player rolls "doubles" three times in a row, they
                immediately move to the "IN JAIL" tile.

-   After moving to their next location, the player will have different
    actions to complete based on the tile type.

    -   A player lands on a "PROPERTY" tile...
        -   If the player is the first person to land on the "PROPERTY"
            tile they can buy the "PROPERTY"
        -   Then, every time another player lands on this "PROPERTY",
            the player has to pay a fee and **the "PROPERTY" generates a
            profit**
            -   This profit is based on the rent of the "PROPERTY"
    -   A player lands on a "RAILROAD" tile...
        -   If the player is the first person to land on the "RAILROAD"
            tile they can buy the "RAILROAD"
        -   Then, every time another player lands on this "RAILROAD",
            the player has to pay a fee and **the "RAILROAD" generates a
            profit**
            -   This profit is based on the number of "RAILROAD" tiles
                owned
    -   A player lands on a "UTILITY" tile...
        -   If the player is the first person to land on the "UTILITY"
            tile they can buy the "UTILITY"
        -   Then, every time another player lands on this "UTILITY", the
            player has to pay a fee and **the "UTILITY" generates a
            unique profit**
            -   This profit is based on the sum of the dice rolled
    -   A player lands on a "CHANCE" or "COMMUNITY CHEST" tile...
        -   The player draws either a "CHANCE" or "COMMUNITY CHEST" card
            based on the type tile they landed on
            -   Then, the player completes the action on the card
        -   **These tiles cannot be bought and cannot generate a
            profit**
    -   A player lands on a "TAX" tile...
        -   The player must pay a fee unique to the tile
        -   **These tiles cannot be bought and cannot generate a
            profit**
    -   A player lands on or passes "GO"...
        -   The player collects "\$200"
        -   **This tile cannot be bought and cannot generate a profit**
    -   A player lands on "IN JAIL"...
        -   There is no action to be completed
        -   **This tile cannot be bought and cannot generate a profit**
    -   A player lands on "GO TO JAIL"...
        -   The player is immediately moved to "IN JAIL"
        -   The player is unable to move forward for the next three
            rolls
        -   **This tile cannot be bought and cannot generate a profit**
    -   A player lands on "FREE PARKING"...
        -   Depending on the version of the game being played, the
            player will either,
            -   collect all money put into "FREE PARKING"
            -   complete no type of action
        -   **This tile cannot be bought and cannot generate a profit**

-   After all players have rolled and moved, the next round begins and
    the process previously stated is repeated.

-   The game ends when three of the four players run out of money and
    the player remaining wins.

## 2. Lets Get Moving:

Build a system that allows for up to 4 players to move around the game
board. As a first attempt, focus on standard dice rolls, ignoring
additional rules related to rolling doubles, jail, or special cards.
Which properties are landed on most frequently? Create a visualization
for this!

```{r}
lets_play(1000,4)

```

\## Findings ###We started with a simple function, lets_move, which
allowed one player to "roll" 2 dice, take the sum, and move the
corresponding distance. The function also allowed the player to loop
back to square 1 if the location was greater than 40, the amount of
squares on the board, then the actual location would be: location-40. We
then made a function, lets_play, that allows multiple players to take
turns "rolling" the dice and moving to a new location. This function
creates a data frame of the players and their positions on the board for
each turn, and plots both density and frequency plots for how often a
player lands on a specific space. Because no specific rules about
rolling doubles or going to jail are incorporated in these function, the
results are as expected. Looking at the frequency plot, space 7 and
spaces which are multiples of 7 tend to be landed on more frequently.
This is the be expected due to the fact that a total of 7 has the
highest probability when rolling 2 die.

Within this section, we also wrote the function, who_goes_first, in
order to determine the starting player order of the game. This function
simulates an initial dice roll by however many players are going to play
the game and incorporates re-rolling for players who tie. The end result
is a list of the players in order of who will go first to be used as an
input for playing the game later.

## 3. Double Down!

Improve your system to incorporate going to jail, including the
doubles-rolling condition. Which properties are landed on most
frequently now? Has this changed dramatically from the previous system
(that didn't account for jail)? Again, visualize this!

```{r}
lets_play2(1000,4)

```

##Findings ###To complete this task we made a new function, lets_move2,
that had the same components as lets_play but added rules when rolling
doubles. If a player rolled a double the new location was recorded and
then they could roll again. The same rule was applied for players that
rolled 2 doubles consecutivley. Once a player rolled 3 doubles in a row
they are sent to jail. To keep players in jail for 3 turns when sent
from "Go to Jail" space or from rolling 3 doubles aspects of the old
lets_play function were also updated in lets_play2. As before, the
dataframe with players and their corresponding positions is outputed as
well as frequency and density plots of these locations. As seen in the
density plot, space 11, is landed on significantly more than the other
spaces. Knowing that space 11 is the jail space on the monopoly board,
this result doesn't come as a suprise. By adding rules about going to
jail when landing on the "Go to Jail" and when rolling 3 doubles in a
row, the jail location is landed on more frequently.

## 4. Take a Chance!

Incorporate the movement cards into your system. You can ignore the
effects of non-movement cards, but not their existence! Which properties
are landed on most frequently now? Has this changed dramatically from
the previous system (that didn't account for Chance)? Again, visualize
this!

```{r}
lets_play3(1000,4)

```

##Findings ###To incorporate the movement cards, chance and community
chest, we created two functions to be added into the previous lets_move2
function. The two new functions allow players to "pick" a random card
out of 16, then a series of if statements are used to direct the player
to their new location. A new if statement was added into a copy of
lets_move2 to allow them to "draw" a card if landing on specific board
locations. The results with the added movement cards have an interesting
affect on the frequency of landing on a space. As previously mentioned,
the most frequent spaces landed on were about 7 spaces apart due to the
probability of the sum of two die. The new frequency plots show that
with the added movement cards these "hot spots" become less frequented
as the movement cards allow players to travel around the board without
relying on the sum of two die. The density plot looks very similar to
the previous plot because space 11 or "Jail" is still the most
frequented space.
