---
title: "Super Awesome Project Template"
output: word_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## libraries
```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```


## Monopoly Movement Rules!
- Before starting the game, it is important to take note of the different types of "equipment" in Monopoly.

### Equipment
#### The Board
- The Board consists of...
  - 40 tiles, each of which have unique actions associated with them based on their type.
  - 16 "CHANCE CARDS"
  - 16 "COMMUNITY CHEST CARDS"
  - 2 six-sided dice

#### Types of Tiles
- "PROPERTY" Tiles
  - There are 8 different sets of properties
  - Each set of properties has...
      - its own color
      - 2 or 3 properties
  - These tiles can bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "RAILROAD" Tiles
  - There are 4 different railroads evenly spaced across the Board
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "UTILITY" Tiles
  - There are two utility tiles
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "CHANCE" Tiles
  - There are 3 chance tiles
  - If one of these tiles is landed on, a "CHANCE CARD" is drawn
    - each of these cards has a specialized action associated with them
    
- "COMMUNITY CHEST" Tiles
  - There are 3 community chest tiles
  - If one of these tiles is landed on, a "COMMUNITY CHEST CHEST" is drawn
    - each of these cards has a specialized action associated with them
    
- "TAX" Tiles
  - There are 2 tax tiles
  - Each of these tiles has a cost associated with them
  
- "GO"
  - This is the first tile
  - Every time this tile is landed on or passed the player collects "$200"
  
- "IN JAIL"

- "GO TO JAIL"
  - When landed on, the player is moved to "IN JAIL"
  
- "FREE PARKING"

### Moving around the Board and Generating Profits

- The first step for beginning the game, even before getting to move the first game piece, is to determine which player will move first.
  - To do this, each player will roll both dice and find the sum of the rolls. The player with the largest sum will start the game. Then the following turn will be the next player.
    - i.e. if Player 2 starts, Player 3 will go next, then Player 4, then Player 4, then back to Player 2, and so on...
    
- All players will start on the "GO" tile.

- To determine how many spaces to move, on their turn each player will roll both dice and find the sum of the rolls. They will then move forward that number of tiles.
  - In the special case of rolling "doubles" (the roll of each die are equal),
      - the player will find the sum of rolls and move forward this number of tiles
      - then, the player will roll again and repeat the previous step.
        - If the player rolls "doubles" again, repeat the previous two steps.
        - If the player rolls "doubles" three times in a row, they immediately move to the "IN JAIL" tile.

- After moving to their next location, the player will have different actions to complete based on the tile type.

  - A player lands on a "PROPERTY" tile...
    - If the player is the first person to land on the "PROPERTY" tile they can buy the "PROPERTY"
    - Then, every time another player lands on this "PROPERTY", the player has to pay a fee and **the "PROPERTY" generates a profit**
        - This profit is based on the rent of the "PROPERTY"
    
  - A player lands on a "RAILROAD" tile...
    - If the player is the first person to land on the "RAILROAD" tile they can buy the "RAILROAD"
    - Then, every time another player lands on this "RAILROAD", the player has to pay a fee and **the "RAILROAD" generates a profit**
      - This profit is based on the number of "RAILROAD" tiles owned 
   
  - A player lands on a "UTILITY" tile...
      - If the player is the first person to land on the "UTILITY" tile they can buy the "UTILITY"
    - Then, every time another player lands on this "UTILITY", the player has to pay a fee and **the "UTILITY" generates a unique profit**
      - This profit is based on the sum of the dice rolled
      
  - A player lands on a "CHANCE" or "COMMUNITY CHEST" tile...
    - The player draws either a "CHANCE" or "COMMUNITY CHEST" card based on the type tile they landed on
      - Then, the player completes the action on the card
    - **These tiles cannot be bought and cannot generate a profit**
    
  - A player lands on a "TAX" tile...
    - The player must pay a fee unique to the tile
    - **These tiles cannot be bought and cannot generate a profit**

  - A player lands on or passes "GO"...
    - The player collects "$200"
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "IN JAIL"...
    - There is no action to be completed
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "GO TO JAIL"...
    - The player is immediately moved to "IN JAIL"
    - The player is unable to move forward for the next three rolls
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "FREE PARKING"...
    - Depending on the version of the game being played, the player will either,
      - collect all money put into "FREE PARKING"
      - complete no type of action
    - **This tile cannot be bought and cannot generate a profit**
        
- After all players have rolled and moved, the next round begins and the process previously stated is repeated.

- The game ends when three of the four players run out of money and the player remaining wins.

##the board
```{r}
monopolyBoard <- read.csv("MonopolyBoard.csv", header = T)
monopolyBoard
```


## lets_move

```{r student1}
# Using dice rolls to determine where a player will land on the board
#input: "location", where the player is on the board
#output: the players new location on the board after the have rolled

#note that this is only accounting for standard dice rolls, no special rules yet...

lets_move = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) #A random roll of a six-sided die
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) #A random roll of a six-sided die
  
  roll_total <- sum(dice_roll_1, dice_roll_2) #The sum of the two rolls
  
  location = location + roll_total #Updating the player's location based on their rolls from the current turn
  
  if(location <= 40) { #if statement checking the players location
    location = location
  } else { #if the sum of the player's previous location and their rolls is greater than 40, this moves the player past GO and the start moving from space 1
    location = location - 40
  }
  
  print(location)
  
}

lets_move(20)
```


## who_goes_first2

```{r student2}

who_goes_first2 <- function(num_players){
  initial_rolls <- c()
  for (i in 1:num_players) {
    player_i_roll <- sum(sample(1:6, 2, replace=TRUE))
    initial_rolls <- c(initial_rolls, player_i_roll) # vector of every player's roll
#    print(paste("Player", i, "rolled", player_i_roll))
  }
  cat("\n")
  if(sum(initial_rolls == max(initial_rolls)) >= 2){
    while (sum(initial_rolls == max(initial_rolls)) >= 2) { # if players tied for highest number
      tied_players <- which(initial_rolls==max(initial_rolls)) # identify which players tied
#      print("It's a tie! Roll again")
#      cat("\n")

#the function "who_goes_first" simulates the initial roll before the game begins in order to determine which player goes first
# input is a number of how many players are going to be playing
# output is a list of players in order of who goes first
who_goes_first2 <- function(num_players){
  initial_rolls <- c()
  player_order <- length(num_players)
  for (i in 1:num_players) {
    player_i_roll <- sum(sample(1:6, 2, replace=TRUE))
    initial_rolls <- c(initial_rolls, player_i_roll) # vector of every player's first roll
  }
  
  if(sum(initial_rolls == max(initial_rolls)) >= 2){ # if more 1 person has the highest roll
    
    while (sum(initial_rolls == max(initial_rolls)) >= 2) { # keep rolling as long as players are tied
      tied_players <- which(initial_rolls==max(initial_rolls)) # identify which players tied

      tie_breaker_rolls <- c()
      for (i in tied_players) { # tied players roll again
       player_i_roll2 <- sum(sample(1:6, 2, replace=TRUE))
       tie_breaker_rolls <- c(tie_breaker_rolls, player_i_roll2)

#       print(paste("Player", i, "rolled", player_i_roll2))
      }
      initial_rolls <- tie_breaker_rolls
      highest_roll <- max(tie_breaker_rolls)
      highest_player2 <- tied_players[which(tie_breaker_rolls == highest_roll)]
    }
#    cat("\n")
#    print(paste("Player", highest_player2, "goes first!"))
  }
  else {
    highest_player <- which.max(initial_rolls) # who rolled the highest number
#    print(paste("Player", highest_player, "goes first!"))
#    return(highest_player)
  
    
  # creating player order
  player_order <- length(num_players)
  player_order[1] <- as.integer(highest_player)

 for (j in 2:num_players) {
    
  player_order[j] <- as.integer(player_order[j-1] + 1)
  if (player_order[j] > num_players) {
    player_order[j] <- 1
  }
 }
  print(player_order)
  }

       initial_rolls <- tie_breaker_rolls # update initial rolls
      }
    }
    highest_roll <- max(tie_breaker_rolls)
    highest_player <- tied_players[which(tie_breaker_rolls == highest_roll)]
  }
  
  else {
    highest_player <- which.max(initial_rolls) # who rolled the highest number
  
    # creating player order
    player_order[1] <- as.integer(highest_player)

    for (j in 2:num_players) {
    
      player_order[j] <- as.integer(player_order[j-1] + 1)
      if (player_order[j] > num_players) {
        player_order[j] <- 1
      }
    }
    #print(player_order)
  }

  playerlist <- (list(highest_player, player_order))
  return(playerlist)
}
```

## lets_play

```{r student3}
#A function to play Monopoly!
#Utilizes lets_move to move the players around the board
#input: "turns"; the amount of turns each player will take (i.e. the number of rounds in the game), "players"; a numeric value 1-4 representing the number of players in the game
#output: a dataframe showing each players' location after each of their turns; a density plot showing each players' location data throughout the game; a density plot showing the overall location data throughout the game

lets_play = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will keep data for locations of players for each turn
  
  # puts players in order
  colnames(location_data) <- who_goes_first2(players)[[2]]
  
  location = 1 #initializes the player at space 1 (i.e. GO!)
  location_data[1,] <- location

  for (i in 2:turns) { # iterates through number of turns
    for (j in 1:players) { # rotates through each player
      location = lets_move(location_data[i-1,j])[[1]] # takes location from lets_move2 function and assigns it to location
      location_data[i,j] <- as.integer(location) # puts location value into the dataframe of locations for each player
    }
  }
print(location_data) 

  

########################## plots ###############################

  #vector of colors
  colors <- c("red", "blue", "green","purple")
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black", xlab="Spaces", main= "Density of Landing Locations for all Players")
  
colors <- c("red", "blue", "green")

  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))

  plot(density(all_spaces), xlim = c(0,40), col = "black", xlab="Spaces", main="Density of Landing Locations for One Player")
  
  #creates frequency plots for landing on each space for each player.
  for(k in 1:players){
  plot(location_data[,k], xlim= c(0,40), col=colors[k], type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
  }
  

  plot(density(all_spaces), xlim = c(0,40), col = "black")

}

lets_play(100, 4)

```



## double_down <- lets_move2

```{r student4}
#Double Down -- addition of jail and double rolls

#Incorporating double rolls and sending players to jail when the players are rolling and moving
#input: "location"; a numeric value 1 to 40; where the player in on the board
#output: the players new location on the board

lets_move2 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) #a standard, six-sided dice roll
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) #a standard, six-sided dice roll
  
  roll_total <- sum(dice_roll_1, dice_roll_2) #the sum of the two dice rolls
  roll_double <- dice_roll_1 == dice_roll_2 #checking if the player rolled a double
  
    location = location + roll_total # updates location to be previous location + roll total
    double3 = "false" # double3 is assigned "true" if the player double rolls 3x (as seen in if statement below), otherwise it is assigned "false" 
    
  # first double roll -> roll again
  if (roll_double == TRUE) { #checks if the player rolled a double with their first two rolls. if "TRUE", the player rolls again
    dice_roll_3 <- sample(1:6, 1, replace = TRUE) #the player's third dice roll
    dice_roll_4 <- sample(1:6, 1, replace = TRUE) #the player's fourth dice roll
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4) #the sum of the player's third and fourth rolls
    roll_double2 <- dice_roll_3 == dice_roll_4 #checks to see if the player rolled a double again
    
    location = location + roll_total2 #the player's new location
    double3 = "false"
    
    # if player is at a location past 40, subtract 40 so they go back to the GO space at location "41"
    # this is included in each if statement below so that it applies if player has to roll again
    if (location <= 40) { #checks to make sure that the player's location isn't over 40 (i.e not on the board)
      location = location
    } else { #If greater than 40, it subtracts 40 from location to allow player to continue to move on the board
      location = location - 40
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) { #if the player has rolled two doubles, they roll again
        dice_roll_5 <- sample(1:6, 1, replace = TRUE) #the player's fifth roll
        dice_roll_6 <- sample(1:6, 1, replace = TRUE) #the player's sixth roll
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6) #the sum of the fifth and sixth roll
        roll_double3 <- dice_roll_5 == dice_roll_6 #checking to see if the player rolled a third double
    
        location = location + roll_total3 #the players new location
        double3 = "false"
        
        if (location <= 40) { #checks the player's location again
          location = location
        } else {
          location = location - 40
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) { #checks if the player rolled three doubles in a row, if TRUE, the players goes to jail (space 11)
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
          }
      }
  }  
    
  if (location <= 40) { #checks the players location on the board
    location = location
  } else {
    location = location - 40
  }
  
  listdata <- (list(location, double3)) # creates list for outputs "location" and "double3"
  # if you need to access location from this function, use lets_move2(location_data[i-1,j])[[1]]
  # if you need to access double3, use lets_move2(double3)[[2]]
  return(listdata)
  
}
```


## lets_play2

```{r}
#A function to move players around the board while incorporating double rolls and going to jail
#input: "turns"; the amount of turns each player takes (i.e. how many rounds the game is), "players"; a numeric value 1-4 representing the number of players in the game
#output: a dataframe showing each players' location after each of their turns; a density plot showing each players' location data throughout the game; a density plot showing the overall location data throughout the game

lets_play2 = function(turns, players) {
  
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will keep data for locations of players for each turn
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will say "true" if player double rolled 3x (which lands them in jail) and "false" if they didn't double roll 3x
  
    # puts players in order
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1 # each player starts at location 1
    location_data[1,] <- location
    double3 = 0 # initializing "double3" which will be later assigned a "true" or "false" based on if player double rolled 3x
  
    for (i in 2:turns) { # iterates through number of turns
      
        for (j in 1:players) { # rotates through each player
          
        location = lets_move2(location_data[i-1,j])[[1]] # takes location from lets_move2 function and assigns it to location
        location_data[i,j] <- as.integer(location) # puts location value into the dataframe of locations for each player
        double3data[i,j] <- lets_move2(double3)[[2]] # takes "true" or "false" value from double3 and adds it to double3data dataframe
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you landed on 31 in the last turn (i-1 turn), you go to jail (space 11) for the ith turn
        location <- 11
        location_data[i,j] <- as.integer(location) # new location is 11
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) { # if you were on space 11 last turn AND you were on space 31 2 turns ago, you stay in jail (space 11) for turn i
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # if player's location is 11 (jail) and double3data is"true" (player double rolled 3x), player stays in jail. all 3 if/else if statements keep player in jail for the next 3 turns
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
  }
  print(location_data)
  print(double3)
  
  
  ########################## plots ###############################

  #vector of colors
  colors <- c("red", "blue", "green","purple")
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black", xlab="Spaces", main= "Density of Landing Locations for all Players")

  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  colors <- c("red", "blue", "green")

  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))

  plot(density(all_spaces), xlim = c(0,40), col = "black", xlab="Spaces", main="Density of Landing Locations for One Player")
  
  #creates frequency plots for landing on each space for each player.
  for(k in 1:players){
  plot(location_data[,k], xlim= c(0,40), col=colors[k], type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
  }

  plot(density(all_spaces), xlim = c(0,40), col = "black")

  
}
 
lets_play2(100, 4)
```
##the community chest and chance cards
```{r}

Card_Numbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16) # the card numbers

Chance_Cards <- c("Advance to Boardwalk", "Advance to Go (Collect $200)", "Advance to Illinois Avenue. If you pass Go, collect $200", "Advance to St. Charles Place. If you pass Go, collect $200", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance token to nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total ten times amount thrown", "Bank pays you dividend of $50", "Get Out of Jail Free", "Go Back 3 Spaces", "Go to Jail. Go directly to Jail, do not pass Go, do not collect $200", "Make general repairs on all your property. For each house pay $25. For each hotel pay $100", "Speeding fine $15", "Take a trip to Reading Railroad. If you pass Go, collect $200", "You have been elected Chairman of the Board. Pay each player $50", "Your building loan matures. Collect $150") # the card information

Chance <- data.frame(Chance_Cards, Card_Numbers) #a dataframe associating each chance card with a number



Community_Chest_Cards <- c("Advance to Go (Collect $200)", "Bank error in your favor. Collect $200", "Doctor’s fee. Pay $50", "From sale of stock you get $50", "Get Out of Jail Free", "Go to Jail. Go directly to jail, do not pass Go, do not collect $200", "Holiday fund matures. Receive $100", "Income tax refund. Collect $20", "It is your birthday. Collect $10 from every player", "Life insurance matures. Collect $100", "Pay hospital fees of $100", "Pay school fees of $50", "Receive $25 consultancy fee", "You are assessed for street repair. $40 per house. $115 per hotel", "You have won second prize in a beauty contest. Collect $10", "You inherit $100") # the card information

Community_Chest <- data.frame(Community_Chest_Cards, Card_Numbers) #a dataframe associating each community chest card with a number
```

##drawing community chest and chance cards
```{r}
#A function that randomly selects a numeric value 1:16 representing a Chance card and updates the player's location based on the card information
#input: "location"; a numeric value 1:40 representing the player's location on the board
#output: the player's new location on the board

Drawing_Chance = function(location) {
  location = location #the player's current location
  draw_card <- sample(1:16, 1, replace = TRUE) #randomly selecting a card from 1:16
  player_card <- Chance$Chance_Cards[draw_card] #finding the card in the Chance deck
  print(player_card)

#The following if statements update the player's location based on the card that was drawn (if applicable)  
      if(draw_card == 1) {
        location = 1
      }
      
      if(draw_card == 2) {
        location = 1
      }
      
      if(draw_card == 3) {
        location = 25
      }
  
      if(draw_card == 4){
        location = 12
      }
    
      if(draw_card == 5){ #takes into account which space the player is nearest to to determine updated location
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 6){ #takes into account which space the player is nearest to to determine updated location
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 7){ #takes into account which space the player is nearest to to determine updated location
        if(location >= 29 && location <= 12){
              location = 13
            } else {
              location = 29
    }
  }
  
    if(draw_card == 11) {
      location = 11
    }
  
    if(draw_card == 14) {
      location = 6
    }
  
    if(draw_card == 10) {
      location = location - 3
    }
  
    location = location
    return(location)
}


#A function that randomly selects a numeric value 1:16 representing a Community Chest card and updates the player's location based on the card information
#input: "location"; a numeric value 1:40 representing the player's location on the board
#output: the player's new location on the board

Drawing_Community_Chest = function(location) {
  location = location #the player's current location
  draw_card_chest <- sample(1:16, 1, replace = TRUE) #randomly selecting a card from 1:16
  player_card_chest <- Community_Chest$Community_Chest_Cards[draw_card_chest] #finding the card in the Community Chest deck
  print(player_card_chest)

#The following if statements update the player's location based on the card that was drawn (if applicable) 
  if (draw_card_chest == 1) {
    location = 1
  } else {
    if (draw_card_chest == 6) {
    location = 11
    } else {
      location = location
    }
  
  }
  
  location = location 
  return(location)
}
```


## lets_move3 -> incorporating chance and community chest spaces and cards
```{r}
#A function that expands on lets_move2 to add the actions of Community Chest and Chance spaces and their respective cards
#input: "location"; a numeric value 1 to 40; where the player in on the board
#output: the players new location on the board

lets_move3 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) 
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) 
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"


  if (location <= 40) {
      location = location
  } else {
      location = location - 40
  }
   
  
  if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
    location = Drawing_Chance(location) #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
  }
  
  if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
    location = Drawing_Community_Chest(location) #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
  }
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"
    
    if (location <= 40) {
      location = location
    } else {
      location = location - 40
    }
    
    
    if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
    location = Drawing_Chance(location) #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
    }
  
  if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
    location = Drawing_Community_Chest(location) #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        
        if (location <= 40) {
          location = location
        } else {
          location = location - 40
        }
        
        if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
          location = Drawing_Chance(location) #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
        }
  
        if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
          location = Drawing_Community_Chest(location) #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
         
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"

          }
      }
  }  
   
  location = location 

  listdata <- (list(location, double3))
  return(listdata)
  
}
```

