---
title: "Super Awesome Project Template"
output: word_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#libraries
library(dplyr)
library(ggplot2)
```

## Monopoly Movement Rules!
- Before starting the game, it is important to take note of the different types of "equipment" in Monopoly.

### Equipment
#### The Board
- The Board consists of...
  - 40 tiles, each of which have unique actions associated with them based on their type.
  - 16 "CHANCE CARDS"
  - 16 "COMMUNITY CHEST CARDS"
  - 2 six-sided dice

#### Types of Tiles
- "PROPERTY" Tiles
  - There are 8 different sets of properties
  - Each set of properties has...
      - its own color
      - 2 or 3 properties
  - These tiles can bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "RAILROAD" Tiles
  - There are 4 different railroads evenly spaced across the Board
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "UTILITY" Tiles
  - There are two utility tiles
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "CHANCE" Tiles
  - There are 3 chance tiles
  - If one of these tiles is landed on, a "CHANCE CARD" is drawn
    - each of these cards has a specialized action associated with them
    
- "COMMUNITY CHEST" Tiles
  - There are 3 community chest tiles
  - If one of these tiles is landed on, a "COMMUNITY CHEST CHEST" is drawn
    - each of these cards has a specialized action associated with them
    
- "TAX" Tiles
  - There are 2 tax tiles
  - Each of these tiles has a cost associated with them
  
- "GO"
  - This is the first tile
  - Every time this tile is landed on or passed the player collects "$200"
  
- "IN JAIL"

- "GO TO JAIL"
  - When landed on, the player is moved to "IN JAIL"
  
- "FREE PARKING"

### Moving around the Board and Generating Profits

- The first step for beginning the game, even before getting to move the first game piece, is to determine which player will move first.
  - To do this, each player will roll both dice and find the sum of the rolls. The player with the largest sum will start the game. Then the following turn will be the next player.
    - i.e. if Player 2 starts, Player 3 will go next, then Player 4, then Player 4, then back to Player 2, and so on...
    
- All players will start on the "GO" tile.

- To determine how many spaces to move, on their turn each player will roll both dice and find the sum of the rolls. They will then move forward that number of tiles.
  - In the special case of rolling "doubles" (the roll of each die are equal),
      - the player will find the sum of rolls and move forward this number of tiles
      - then, the player will roll again and repeat the previous step.
        - If the player rolls "doubles" again, repeat the previous two steps.
        - If the player rolls "doubles" three times in a row, they immediately move to the "IN JAIL" tile.

- After moving to their next location, the player will have different actions to complete based on the tile type.

  - A player lands on a "PROPERTY" tile...
    - If the player is the first person to land on the "PROPERTY" tile they can buy the "PROPERTY"
    - Then, every time another player lands on this "PROPERTY", the player has to pay a fee and **the "PROPERTY" generates a profit**
        - This profit is based on the rent of the "PROPERTY"
    
  - A player lands on a "RAILROAD" tile...
    - If the player is the first person to land on the "RAILROAD" tile they can buy the "RAILROAD"
    - Then, every time another player lands on this "RAILROAD", the player has to pay a fee and **the "RAILROAD" generates a profit**
      - This profit is based on the number of "RAILROAD" tiles owned 
   
  - A player lands on a "UTILITY" tile...
      - If the player is the first person to land on the "UTILITY" tile they can buy the "UTILITY"
    - Then, every time another player lands on this "UTILITY", the player has to pay a fee and **the "UTILITY" generates a unique profit**
      - This profit is based on the sum of the dice rolled
      
  - A player lands on a "CHANCE" or "COMMUNITY CHEST" tile...
    - The player draws either a "CHANCE" or "COMMUNITY CHEST" card based on the type tile they landed on
      - Then, the player completes the action on the card
    - **These tiles cannot be bought and cannot generate a profit**
    
  - A player lands on a "TAX" tile...
    - The player must pay a fee unique to the tile
    - **These tiles cannot be bought and cannot generate a profit**

  - A player lands on or passes "GO"...
    - The player collects "$200"
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "IN JAIL"...
    - There is no action to be completed
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "GO TO JAIL"...
    - The player is immediately moved to "IN JAIL"
    - The player is unable to move forward for the next three rolls
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "FREE PARKING"...
    - Depending on the version of the game being played, the player will either,
      - collect all money put into "FREE PARKING"
      - complete no type of action
    - **This tile cannot be bought and cannot generate a profit**
        
- After all players have rolled and moved, the next round begins and the process previously state is repeated.

- The game ends when three of the four players run out of money.

## Section One

```{r student1}
#Kayleigh
##LET'S GET MOVING

monopolyBoard <- read.csv("MonopolyBoard.csv", header = T)
monopolyBoard

# Using dice rolls to determine where a player will land on the board
#input: "location"; a number 1-40; where the player is on the board
#output: the amount of spaces the player will move until they are on their new location

#note that this is only accounting for standard dice rolls, no special rules yet...

lets_move = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    
  if (location <= 40) {
    location = location
  } else {
    location = location - 40
  }
  
  space = monopolyBoard$name[monopolyBoard$spaces == location]
  
  print("You're moving forward...")
  print(roll_total)
  
  print("You're on space...")
  print(location)
  
  #print(space) #This prints out the name of the space that they land on. 
}

#testers
lets_move(1)
lets_move(25)
lets_move(38)
lets_move(40)



#A function to move players around the board and to play Monopoly!
#input: "turns"; the amount of turns we should take
#output: a player's new location on the board

lets_play = function(turns) {
  location = 1
  print("Starting Location: GO!")
  for (i in 1:turns) {
    location = lets_move(location)
  }
  print("You've landed on...")
  return(location)
}



lets_play(10) #tester #in this example if you look at a reference monopoly board and "walk" your way around the board with each move being the number in each output, you'll land on the space on the board corresponding to the final output (when counting "GO" as 1 and/or 40) 

#testers 
#"lets_move" and "lets_play" have both been edited to print out phrases for each roll and move to make it easier to determine how the player is moving. 
#"You're moving forward..." gives the player's roll
#"You're on space..." is the players position after 1 turn/"lets_move"
  # Later try to switch this print statement to the name of the spot that the player is on 
#"You've landed on..." gives the final location after running "lets_play" for "x" turns.
  # Later try to switch this print statement to the name of the spot that the player is on 

lets_play(3)
lets_play(10)

```

```{r}
##DOUBLE DOWN

##WORK IN PROGRESS

#A function using dice rolls to determine how many spaces a player will move with the additional rules for "doubles" in Monopoly
#input: "location"; a number 1-40 where the player is on the board
#outut: the number of spaces the player will move on the board, with the special case of rolling three "doubles" and landing in jail
double_down = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
  print("roll was")
  print(roll_total)
    
  if (roll_double) {
    
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total_2 <- sum(dice_roll_3, dice_roll_4)
    roll_double_2 <- dice_roll_3 == dice_roll_4
    
    print("roll double was")
    print(roll_total_2)

    
    if (roll_double_2) {
      dice_roll_5 <- sample(1:6, 1, replace = TRUE)
      dice_roll_6 <- sample(1:6, 1, replace = TRUE)
      
      roll_total_3 <- sum(dice_roll_5, dice_roll_6)
      roll_double_3 <- dice_roll_5 == dice_roll_6
      
      print("roll double was")
      print(roll_total_3)
      
      if (roll_double_3) {
        location = 11 #Jail
        print("doubles, doubles, doubles")
        print("You're going to JAIL!")
        
      } else {
        location = location + roll_total + roll_total_2 + roll_total_3
        print("doubles, doubles, not doubles")
        print("You're moving forward...")
        print(roll_total + roll_total_2 + roll_total_3)
      }
    } else {
      location = location + roll_total + roll_total_2
      print("doubles, not doubles")
      print("You're moving forward...")
      print(roll_total+roll_total_2)
    }
  } else {
    location = location + roll_total
    print("no doubles")
    print("You're moving forward...")
    print(roll_total)
  }

    
  if (location <= 40) {
    location = location
  } else {
    location = location - 40
  }

  
  print("You're on space...")
  print(location)
}

double_down(1)
#text out in the function is kinda funky right but it's just to make sure its working right
#In final version switch all dice rolls to sample(1:6,...)

```


```{r}
##CHANCE AND COMMUNITY CHEST CARDS
Card_Numbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16)

Chance_Cards <- c("Advance to Boardwalk", "Advance to Go (Collect $200)", "Advance to Illinois Avenue. If you pass Go, collect $200", "Advance to St. Charles Place. If you pass Go, collect $200", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance token to nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total ten times amount thrown", "Bank pays you dividend of $50", "Get Out of Jail Free", "Go Back 3 Spaces", "Go to Jail. Go directly to Jail, do not pass Go, do not collect $200", "Make general repairs on all your property. For each house pay $25. For each hotel pay $100", "Speeding fine $15", "Take a trip to Reading Railroad. If you pass Go, collect $200", "You have been elected Chairman of the Board. Pay each player $50", "Your building loan matures. Collect $150")

Chance <- data.frame(Chance_Cards, Card_Numbers)
Chance
##Chance cards to move a player to a new space:
  #1 -> Advance to Boardwalk (space 40)
  #2 -> Advance to Go (space 1)
  #3 -> Advance to Illinois Avenue (space 25)
  #4 -> Advance to St. Charles Place (space 12)
  #5 -> Advance to nearest Railroad (space(s) 6, 16, 26, 36)
  #6 -> Advance to nearest Railraod (space(s) 6, 16, 26, 36)
  #7 -> Advance to nearest Utility (space(s) 13, 29)
  #11 -> Go to Jail (space 11)
  #14 -> Take a trip to Reading Railroad (space 6)

Community_Chest_Cards <- c("Advance to Go (Collect $200)", "Bank error in your favor. Collect $200", "Doctor’s fee. Pay $50", "From sale of stock you get $50", "Get Out of Jail Free", "Go to Jail. Go directly to jail, do not pass Go, do not collect $200", "Holiday fund matures. Receive $100", "Income tax refund. Collect $20", "It is your birthday. Collect $10 from every player", "Life insurance matures. Collect $100", "Pay hospital fees of $100", "Pay school fees of $50", "Receive $25 consultancy fee", "You are assessed for street repair. $40 per house. $115 per hotel", "You have won second prize in a beauty contest. Collect $10", "You inherit $100")

Community_Chest <- data.frame(Community_Chest_Cards, Card_Numbers)
Community_Chest

##Community Chest Cards that move a player to a new space:
  #1 -> Advance to GO (space 1)
  #5 -> Go to Jail (space 11)

```


## Section Two

```{r student2}
# heidi

#the function "who_goes_first" simulates the initial roll before the game begins in order to determine which player goes first
# input is a number of how many players are going to be playing
# output is the value of each players roll and the player that will start the game based on who had the highest roll
who_goes_first <- function(num_players){
  initial_rolls <- c()
  for (i in 1:num_players) {
    player_i_roll <- sum(sample(1:6, 2, replace=TRUE))
    initial_rolls <- c(initial_rolls, player_i_roll) # vector of every player's roll
    print(paste("Player", i, "rolled", player_i_roll))
  }
  cat("\n")
  if(sum(initial_rolls == max(initial_rolls)) >= 2){
    while (sum(initial_rolls == max(initial_rolls)) >= 2) { # if players tied for highest number
      tied_players <- which(initial_rolls==max(initial_rolls)) # identify which players tied
      print("It's a tie! Roll again")
      cat("\n")
      tie_breaker_rolls <- c()
      for (i in tied_players) { # tied players roll again
       player_i_roll2 <- sum(sample(1:6, 2, replace=TRUE))
       tie_breaker_rolls <- c(tie_breaker_rolls, player_i_roll2)
       print(paste("Player", i, "rolled", player_i_roll2))
      }
      initial_rolls <- tie_breaker_rolls
      highest_roll <- max(tie_breaker_rolls)
      highest_player2 <- tied_players[which(tie_breaker_rolls == highest_roll)]
    }
    cat("\n")
    print(paste("Player", highest_player2, "goes first!"))
  }
  else {
    highest_player <- which.max(initial_rolls) # who rolled the highest number
    print(paste("Player", highest_player, "goes first!"))
  }
}

who_goes_first(4) # test function

```

## Section Three

```{r student3}
# Olivia
# Website for data: https://stat-jet-asu.github.io/Datasets/InstructorDescriptions/monopoly.html

monopolyBoard <- read.csv("MonopolyBoard.csv", header = T)
head(monopolyBoard)

# This section is for question number 2

# Kayleigh's lets_play function from above incorporating players and density plots
# uses lets_move function from above
# input: turns, # of turns to iterate through; players, number of players (2-4)
# output: density plot with a line for each player's frequency of spaces landed on 
# & density plot for the combined frequency of spaces landed on for all players

lets_play = function(turns, players) {
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  
for (j in 1:players) {
  location = 1
  
  for (i in 1:turns) {
    
    location = lets_move(location)
    location_data[i,j] <- location
    }
  }
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  colors <- c("red", "blue", "green")
  
  for (k in 2:players) {
  lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  plot(density(all_spaces), xlim = c(0,40), col = "black")
}
lets_play(100, 4)

```


```{r}
who_goes_first2 <- function(num_players){
  initial_rolls <- c()
  for (i in 1:num_players) {
    player_i_roll <- sum(sample(1:6, 2, replace=TRUE))
    initial_rolls <- c(initial_rolls, player_i_roll) # vector of every player's roll
#    print(paste("Player", i, "rolled", player_i_roll))
  }
  cat("\n")
  if(sum(initial_rolls == max(initial_rolls)) >= 2){
    while (sum(initial_rolls == max(initial_rolls)) >= 2) { # if players tied for highest number
      tied_players <- which(initial_rolls==max(initial_rolls)) # identify which players tied
#      print("It's a tie! Roll again")
#      cat("\n")
      tie_breaker_rolls <- c()
      for (i in tied_players) { # tied players roll again
       player_i_roll2 <- sum(sample(1:6, 2, replace=TRUE))
       tie_breaker_rolls <- c(tie_breaker_rolls, player_i_roll2)
#       print(paste("Player", i, "rolled", player_i_roll2))
      }
      initial_rolls <- tie_breaker_rolls
      highest_roll <- max(tie_breaker_rolls)
      highest_player2 <- tied_players[which(tie_breaker_rolls == highest_roll)]
    }
#    cat("\n")
#    print(paste("Player", highest_player2, "goes first!"))
  }
  else {
    highest_player <- which.max(initial_rolls) # who rolled the highest number
#    print(paste("Player", highest_player, "goes first!"))
#    return(highest_player)
  
    
  # creating player order
  player_order <- length(num_players)
  player_order[1] <- as.integer(highest_player)

 for (j in 2:num_players) {
    
  player_order[j] <- as.integer(player_order[j-1] + 1)
  if (player_order[j] > num_players) {
    player_order[j] <- 1
  }
 }
  print(player_order)
  }
  
  playerlist <- (list(highest_player, player_order))
  return(playerlist)
}

#who_goes_first2(4)

```


```{r}
# Question number 3 -- including jail and double rolls

lets_move2 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total # updates location to be previous location + roll total
    double3 = "false" # double3 is assigned "true" if the player double rolls 3x (as seen in if statement below), otherwise it is assigned "false" 
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"
    
    # if player is at a location past 40, subtract 40 so they go back to the GO space at location "41"
    # this is included in each if statement below so that it applies if player has to roll again
    if (location <= 40) {
      location = location
    } else {
      location = location - 40
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        
        if (location <= 40) {
          location = location
        } else {
          location = location - 40
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
          }
      }
  }  
    
  if (location <= 40) {
    location = location
  } else {
    location = location - 40
  }
  
  listdata <- (list(location, double3)) # creates list for outputs "location" and "double3"
  # if you need to access location from this function, use lets_move2(location)[[1]]
  # if you need to access double3, use lets_move2(double3)[[2]]
  return(listdata)
  
}


# lets_play2 is currently set up to have each player go thru all their turns and then move onto the next player
# probably need to fix this for question 5

```

```{r}

lets_play2 = function(turns, players) {
  
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will keep data for locations of players for each turn
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will say "true" if player double rolled 3x (which lands them in jail) and "false" if they didn't double roll 3x
  
    # puts players in order
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1 # each player starts at location 1
    location_data[1,] <- location
    double3 = 0 # initializing "double3" which will be later assigned a "true" or "false" based on if player double rolled 3x
  
    for (i in 2:turns) { # iterates through number of turns
      
        for (j in 1:players) { # rotates through each player
          
        location = lets_move2(location_data[i-1,j])[[1]] # takes location from lets_move2 function and assigns it to location
        location_data[i,j] <- as.integer(location) # puts location value into the dataframe of locations for each player
        double3data[i,j] <- lets_move2(double3)[[2]] # takes "true" or "false" value from double3 and adds it to double3data dataframe
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you landed on 31 in the last turn (i-1 turn), you go to jail (space 11) for the ith turn
        location <- 11
        location_data[i,j] <- as.integer(location) # new location is 11
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) { # if you were on space 11 last turn AND you were on space 31 2 turns ago, you stay in jail (space 11) for turn i
        location <- 11
        location_data[i,j] <- as.integer(location)  
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # if player's location is 11 (jail) and double3data is"true" (player double rolled 3x), player stays in jail. all 3 if/else if statements keep player in jail for the next 3 turns
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
  }
  print(location_data)
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  colors <- c("red", "blue", "green")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  plot(density(all_spaces), xlim = c(0,40), col = "black")
  
}
 
lets_play2(10, 3)

location_data

# how should we go about recording spaces landed on when double rolls occur?

```


```{r}
# olivia (ignore this its a work in progress)
# Figure out how to have players pay and recieve money from landing on chance and community chest spaces

     if(draw_card == 5){
        if(location >= 37 && location <= 5){
              location = 6
              
              
            } else if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
  
    if(draw_card == 6){
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }

#################

Updating_Player_Bank <- function(location) {
  if(location == 2 || location == 4 || location == 6 || location == 7 || location == 9 || location == 10 || location == 12 || location == 13 || location == 14 || location == 15 || location == 16 || location == 17 || location == 19 || location == 20 || location == 22 || location == 24 || location == 25 || location == 26 || location == 27 || location == 28 || location == 29 || location == 30 || location == 32 || location == 33 || location == 35 || location == 36 || location == 38 || location == 40){
    location = location
    spot <- which(Property_Statuses$Space == location)
    cost <- which(monopolyBoard$spaces == location)
    owned_by_player <- Property_Statuses$Owned_By_Player[spot]
#    The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_0[cost]
#    The_Players$Player_Bank[owned_by_player]
#    print(The_Players)
#    print(owned_by_player)
#    print(cost)
    
#    The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_0[cost]
    
#    The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_0[cost]
    
    bank_list <- list(owned_by_player, cost)
    return(bank_list)

  }
}

Updating_Player_Bank(15)

#########################################

lets_move3 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"
  
#  print("your roll total is...")
#  print(roll_total)

  if (location <= 40) {
      location = location
  } else {
      location = location - 40
  }
   
#  print("your location is...")
#  print(location)
  
#  Updating_Player_Bank(location)
  
  if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
#    print("your location is...")
#    print(location)
#    Updating_Player_Bank(location)
  }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
#    print("your location is...")
#    print(location)
#    Updating_Player_Bank(location)
  }
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"
#    print("1 double")
    
    if (location <= 40) {
      location = location
    } else {
      location = location - 40
    }
    
    
    if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
  }
    
#    Updating_Player_Bank(location)
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
#        print("2 doubles")
        
        if (location <= 40) {
          location = location
        } else {
          location = location - 40
        }
        
        
        if(location == 8 || location == 23 || location == 27) {
          location = Drawing_Chance(location)
        }
  
        if(location == 3 || location == 18 || location == 34) {
          location = Drawing_Community_Chest(location)
         
        }
        
#        Updating_Player_Bank(location)
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
#            print("three doubles")
          }
      }
  }  
   
  location = location 
  
#  print("your location is...")
#  print(location)
  listdata <- (list(location, double3, The_Players))
  return(listdata)
  
}

##########

# replaces NAs in rent_0 column with 0s
monopolyBoard$rent_0[is.na(monopolyBoard$rent_0) == TRUE] <- as.integer(0)

lets_play_idk = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
#  player_bank_amount <- 0
#  player_bank_data <- data.frame(matrix(nrow = 2, ncol = players))
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move3(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move3(double3)[[2]]
        
  #      player_bank_amount <- lets_move3(location_data[i-1,j])[[3]]
  #      player_bank_data <- as.integer(player_bank_amount)
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
        
      owned_by_player <- Updating_Player_Bank(location)[[1]]
      cost <- Updating_Player_Bank(location)[[2]]
      The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_0[cost]
      The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_0[cost]
#  return(The_Players)
    }
  }
  print(location_data)
  print(double3data)
#  print(player_bank_data)
  print(The_Players)
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  plot(location_data[,1], xlim= c(0,40), col="black", type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
  
  colors <- c("red", "blue", "green")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  plot(density(all_spaces), xlim = c(0,40), col = "black")
 
}

lets_play_idk(10, 4)

```



```{r}
#4 - Kayleigh and Maddie 
#Chance - spaces 8, 23, 37
#Community Chest - spaces 3, 18, 34
Chance

Drawing_Chance = function(location) {
  location = location
  draw_card <- sample(1:16, 1, replace = TRUE)
  player_card <- Chance$Chance_Cards[draw_card]
  print(player_card)

  
      if(draw_card == 1) {
        location = 1
      }
      
      if(draw_card == 2) {
        location = 1
      }
      
      if(draw_card == 3) {
        location = 25
      }
  
      if(draw_card == 4){
        location = 12
      }
  
      if(draw_card == 5){
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 6){
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 7){
        if(location >= 29 && location <= 12){
              location = 13
            } else {
              location = 29
    }
  }
  
    if(draw_card == 11) {
      location = 11
    }
  
    if(draw_card == 14) {
      location = 6
    }
  
    if(draw_card == 10) {
      location = location - 3
    }
  
    location = location
    return(location)
}

Drawing_Chance(8)
Drawing_Chance(23)
Drawing_Chance(37)

Drawing_Community_Chest = function(location) {
  location = location
  draw_card_chest <- sample(1:16, 1, replace = TRUE)
  player_card_chest <- Community_Chest$Community_Chest_Cards[draw_card_chest]
  print(player_card_chest)
  print(location)
  
  if (draw_card_chest == 1) {
    location = 1
  } else {
    if (draw_card_chest == 6) {
    location = 11
    } else {
      location = location
    }
  
  }
  
  location = location 
  return(location)
}

Drawing_Community_Chest(3)
Drawing_Community_Chest(18)
Drawing_Community_Chest(34)

lets_move3 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"
  
  print("your roll total is...")
  print(roll_total)

  if (location <= 40) {
      location = location
  } else {
      location = location - 40
  }
   
  print("your location is...")
  print(location)
  
  if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    print("your location is...")
    print(location)
  }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
    print("your location is...")
    print(location)
  }
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"
    print("1 double")
    
    if (location <= 40) {
      location = location
    } else {
      location = location - 40
    }
    
    
    if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        print("2 doubles")
        
        if (location <= 40) {
          location = location
        } else {
          location = location - 40
        }
        
        if(location == 8 || location == 23 || location == 27) {
          location = Drawing_Chance(location)
        }
  
        if(location == 3 || location == 18 || location == 34) {
          location = Drawing_Community_Chest(location)
         
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
            print("three doubles")
          }
      }
  }  
   
  location = location 
  
  print("your location is...")
  print(location)
  listdata <- (list(location, double3))
  return(listdata)
  
}

lets_move3(1)


lets_play3 = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move3(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move3(double3)[[2]]
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
  }
  print(location_data)
  print(double3data)


  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  
  plot(location_data[,1], xlim= c(0,40), col="black", type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
  
  colors <- c("red", "blue", "green")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  plot(density(all_spaces), xlim = c(0,40), col = "black")
  
}


lets_play3(100, 4)

```


## Section Four

```{r student4}

#use lets_move2 for freq plot

 
```

## Section Five
```{r student5}
#hello
dice_roll <- sum(sample(1:6, 2, replace = TRUE))
dice_roll

Drawing_Chance = function(location) {
  location = location
  draw_card <- sample(1:16, 1, replace = TRUE)
  player_card <- Chance$Chance_Cards[draw_card]
  print(player_card)

  
      if(draw_card == 1) {
        location = 1
      }
      
      if(draw_card == 2) {
        location = 1
        Player_Bank = Player_Bank + 200
      }
      
      if(draw_card == 3) {
        if(location > 25){
          Player_Bank = Player_Bank + 200
        }else{
          Player_Bank = Player_Bank
    }
        location = 25
      }
  
      if(draw_card == 4){
        if(location > 13 ){
          Player_Bank = Player_Bank + 200
        }else{
          Player_Bank = Player_Bank
    }
        location = 12
      }
  
      if(draw_card == 5){
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 6){
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 7){
        if(location >= 29 && location <= 12){
              location = 13
            } else {
              location = 29
    }
    }
  
    if(draw_card == 8){
      Player_Bank = Player_Bank + 50
    }
  
    if(draw_card == 10) {
      location = location - 3
    }
  
    if(draw_card == 11) {
      location = 11
    }
  
    if(draw_card == 13){
      Player_Bank = Player_Bank - 15
    }
  
    if(draw_card == 14) {
      if(location > 6){
        Player_Bank = Player_Bank + 200
      }else{
        Player_Bank = Player_Bank
    }
      location = 6
    }
  
    if(draw_card == 16){
      Player_Bank = Player_Bank + 150
    }
  
   
    location = location
    return(location)
}

Drawing_Community_Chest = function(location) {
  location = location
  draw_card_chest <- sample(1:16, 1, replace = TRUE)
  player_card_chest <- Community_Chest$Community_Chest_Cards[draw_card_chest]
  print(player_card_chest)
  print(location)
  
  
  if (draw_card_chest == 1) {
    location = 1
    Player_Bank = Player_Bank + 200
  }
  
  #Bank error in your favor. Collect $200
  if(draw_card == 2){
    Player_Bank = Player_Bank + 200
  }
  
  #Doctor’s fee. Pay $50
  if(draw_card == 3){
    Player_Bank = Player_Bank - 50
  }
  
  #From sale of stock you get $50
  if(draw_card == 4){
    Player_Bank = Player_Bank + 50
  }
  
  if(draw_card_chest == 6) {
    location = 11
  }
  
  #Holiday fund matures. Receive $100
  if(draw_card == 7){
    Player_Bank = Player_Bank + 100
  }
  
  #Income tax refund. Collect $20
  if(draw_card == 8){
    Player_Bank = Player_Bank + 20
  }
  
  #Life insurance matures. Collect $100
  if(draw_card == 10){
    Player_Bank = Player_Bank + 100
  }
  
  #Pay hospital fees of $100
  if(draw_card == 11){
    Player_Bank = Player_Bank - 100
  }
  
  #Pay school fees of $50
  if(draw_card == 12){
    Player_Bank = Player_Bank - 50
  }
  
  #Receive $25 consultancy fee
  if(draw_card == 13){
    Player_Bank = Player_Bank + 25
  }
  
  #You have won second prize in a beauty contest. Collect $10
  if(draw_card == 15){
    Player_Bank = Player_Bank + 10
  }
  
  #You inherit $100
  if(draw_card == 16){
    Player_Bank = Player_Bank + 100
  }
  
  location = location 
  return(location)
}



Chance
Community_Chest
```

_Play a Game_
- players funds
  - adding to players funds
  - subtracting from players funds
  - player losing once funds = 0

- buying properties
- paying rent when landing on an owned property

```{r}
library(tidyverse)
```

```{r}
Players <- c("Player 1", "Player 2", "Player 3", "Player 4")
Player_Bank <- c(1250, 1250, 1250, 1250)
The_Players <- data.frame(Players, Player_Bank)

Property <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Connecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")
Owned_By_Player <- sample(1:4, 28, replace = TRUE)
Space <- c(2, 4, 6, 7, 9, 10, 12, 13, 14, 15, 16, 17, 19, 20, 22, 24, 25, 26, 27, 28, 29, 30, 32, 33, 35, 36, 38, 40)
Property_Statuses <- data.frame(Property, Space, Owned_By_Player)
Property_Statuses


Updating_Player_Bank <- function(location, j) {
  if(location == 2 || location == 4 || location == 6 || location == 7 || location == 9 || location == 10 || location == 12 || location == 13 || location == 14 || location == 15 || location == 16 || location == 17 || location == 19 || location == 20 || location == 22 || location == 24 || location == 25 || location == 26 || location == 27 || location == 28 || location == 29 || location == 30 || location == 32 || location == 33 || location == 35 || location == 36 || location == 38 || location == 40){
    
    location = location
    spot <- which(Property_Statuses$Space == location)
    cost <- which(monopolyBoard$spaces == location)
    owned_by_player <- Property_Statuses$Owned_By_Player[spot]
    
    The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_0[cost]
    
    The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_0[cost]
    
    The_Players
  }
}

Updating_Player_Bank(2, 3)

lets_move3 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"


  if (location <= 40) {
      location = location
  } else {
      location = location - 40
  }

  if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)

  }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)

  }

Updating_Player_Bank(location, j)

  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"

    
    if (location <= 40) {
      location = location
    } else {
      location = location - 40
    }
    
    
    if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
    }
    
    Updating_Player_Bank(location, j)
    
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        
        if (location <= 40) {
          location = location
        } else {
          location = location - 40
        }
        
        if(location == 8 || location == 23 || location == 27) {
          location = Drawing_Chance(location)
        }
  
        if(location == 3 || location == 18 || location == 34) {
          location = Drawing_Community_Chest(location)
         
        }
        
        Updating_Player_Bank(location, j)
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
          }
      }
  }  
   
  location = location 
}

lets_move3(2)


lets_play4 = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  players_banks <- as.data.frame(matrix(nrow = turns, ncol = players))

print(Property_Statuses)

  for (j in 1:players) {
    location = 1
    double3 = 0
    
    
    for (i in 1:turns) {
        print("player")
        print(j)
        location = lets_move3(location)[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move3(double3)[[2]]

                
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
      
      
    }
  }
  
print(location_data)
return(The_Players)

}

lets_play4(1,4)
```


```{r}
monopolyBoard
Players <- c("Player 1", "Player 2", "Player 3", "Player 4")
Player_Bank <- c(1250, 1250, 1250, 1250)
The_Players <- data.frame(Players, Player_Bank)

Property <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Connecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")
Owned_By_Player <- sample(1:4, 28, replace = TRUE)
Space <- c(2, 4, 6, 7, 9, 10, 12, 13, 14, 15, 16, 17, 19, 20, 22, 24, 25, 26, 27, 28, 29, 30, 32, 33, 35, 36, 38, 40)
Property_Statuses <- data.frame(Property, Space, Owned_By_Player)
Property_Statuses


Updating_Player_Bank <- function(location, j) {
  if(location == 2 || location == 4 || location == 6 || location == 7 || location == 9 || location == 10 || location == 12 || location == 13 || location == 14 || location == 15 || location == 16 || location == 17 || location == 19 || location == 20 || location == 22 || location == 24 || location == 25 || location == 26 || location == 27 || location == 28 || location == 29 || location == 30 || location == 32 || location == 33 || location == 35 || location == 36 || location == 38 || location == 40){
    location = location
    spot <- which(Property_Statuses$Space == location)
    cost <- which(monopolyBoard$spaces == location)
    owned_by_player <- Property_Statuses$Owned_By_Player[spot]
    The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$cost[cost]
    The_Players$Player_Bank[owned_by_player]
    The_Players
    
    The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_0[cost]
    
    The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_0[cost]
    
    return(The_Players)

  }
}

Updating_Player_Bank(12, 3)
```


```{r}
lets_move4 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"
    
    j=2

  if (location <= 40) {
      location = location
      Updating_Player_Bank(location, j)
  } else {
      location = location - 40
      Updating_Player_Bank(location, j)
  }


  if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    Updating_Player_Bank(location, j)

  }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
    Updating_Player_Bank(location, j)

  }


  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"

    
    if (location <= 40) {
      location = location
      Updating_Player_Bank(location, j)
      
    } else {
      location = location - 40
      Updating_Player_Bank(location, j)
    }
    
    
    if(location == 8 || location == 23 || location == 27) {
    location = Drawing_Chance(location)
    Updating_Player_Bank(location, j)
    }
  
  if(location == 3 || location == 18 || location == 34) {
    location = Drawing_Community_Chest(location)
    Updating_Player_Bank(location, j)
    }

    
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        
        if (location <= 40) {
          location = location
          Updating_Player_Bank(location, j)
        } else {
          location = location - 40
          Updating_Player_Bank(location, j)
        }
        
        if(location == 8 || location == 23 || location == 27) {
          location = Drawing_Chance(location)
          Updating_Player_Bank(location, j)
        }
  
        if(location == 3 || location == 18 || location == 34) {
          location = Drawing_Community_Chest(location)
          Updating_Player_Bank(location, j)
         
        }

        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
          }
      }
  }  
   
  location = location 
  
  listdata <- (list(location, double3))
  return(listdata)
  return(Updating_Player_Bank(location, j))
  
}

lets_move4(12)
lets_move4(Updating_Player_Bank())
```


```{r}

lets_play4 = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move4(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move4(double3)[[2]]
        print(j)
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
    }
    
  print(location_data)
  print(double3data)
  print(The_Players)
    
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black")
  plot(location_data[,1], xlim= c(0,40), col="black", type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
  
  colors <- c("red", "blue", "green")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  plot(density(all_spaces), xlim = c(0,40), col = "black")

}

lets_play4(10, 4)

```

